\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}

\title{%
  Game Theory: Homework 4 \\
  \large Silvan Hungerbuehler, 11394013}

\usepackage{mathptmx} % "times new roman"
\usepackage{amssymb}
\usepackage{amsmath, amsthm}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{comment}
\usepackage[margin=1in]{geometry}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{bm}

\usepackage[normalem]{ulem}
\date{}
\begin{document}
\maketitle

\section*{Question 1}
\subsection*{a}
\begin{align*}
N=&\{1,2\} \\
A=&\{small,pass,medium,big\} \\
H=&\{A,B\}  &\text{$A$ is the root and $B$ the second player's choice node.}\\
Z=&\{C,D,E\} \\
\underline{i}=&\begin{cases}
A\rightarrow 1 \\
B \rightarrow 2 
\end{cases}&\underline{i}: H\rightarrow N,\text{ maps internal nodes to players} \\
\underline{A}=&\begin{cases}
A\rightarrow\{small,pass\} \\
B\rightarrow\{medium,big\} 
\end{cases} &\underline{A}:H\rightarrow 2^A,\text{ maps internal nodes to available actions} \\
\sigma=& \begin{cases}
\{A,small\}\rightarrow E \\
\{A,pass\}\rightarrow B\\
\{B,medium\}\rightarrow C\\
\{B,big\}\rightarrow D
\end{cases}  &\sigma :H\times A\rightarrow H\cup Z\\
u=&(u_1,u_2)\\
&u_1=\begin{cases}
E\rightarrow 10\\
C\rightarrow 20\\
D\rightarrow 0
\end{cases}\\
&u_2=\begin{cases}
E\rightarrow 0\\
C\rightarrow 20\\
D\rightarrow 30
\end{cases}
\end{align*}
\subsection*{b \& c}
Consider the following translation to normal-form:
\begin{table}[h]
\centering
\begin{tabular}[l]{|l|l|l|}
\hline
          & $Medium$ & $Big$  \\ \hline
$Small$     & 10, 0   & 10, 0 \\ \hline
$Pass$	& 20,20 & 0, 30 \\ \hline
\end{tabular}
\end{table}
\noindent The only pure (subgame-perfect) NE is $(S,B)$. Since $Big$ strictly dominates $Medium$ for Colin, he therefore won't deviate. And Rowena has no incentive to do so either in that strategy profile, because $10>0$. Note that we have found the only(!) pure NE by inspecting the normal-form. In this case this is not an issue because we have found only one NE. Since there must be one subgame-perfect NE, the possibility of this being a non-subgame-perfect NE in the normal-form is excluded. (Backwards-induction yields the same pure NE.)
\subsection*{d} 
Let $p$ denote Player 1's probability of playing $Small$ and $q$ Player 2's probability of playing $Medium$. We get the the following mixed and pure NE:\\
 $[(1,0),(q,1-q)]$, where $q\leq 0.5\in [0,1]$.\\
$[(1,0),(0,1)]$, as determined above.
\section*{Question 2}
We want to translate a two-player, normal-form game to an extensive-form game with imperfect information.\\
$<N',\boldsymbol{A}',\boldsymbol{u}'> \implies <N,\boldsymbol{A}, H, Z, \underline{i},\underline{A},\sigma,\boldsymbol{u},\sim>$

\noindent The following elements in the extensive-game tuple are straightforward to translate. Note that $1^*$ denotes a special node - the root - while $1^{\#}$ is a regular terminal node like any other element in $Z$.
 \begin{align*}
&N' \implies N & N=\{1,2\} \text{ by assumption}\\
&\boldsymbol{A}'=\{A_1,A_2\} \implies \Cup_i A_i &\text{} \\
&H=\{1^*,...,(1+|A_1|)^*\} &\text{$1^*$ denotes the root, the rest are choice nodes for Player 2} \\
&\sim=(\sim_1,\sim_2), \text{ where $\sim_1=1^*$ and $\sim_2=H-\{1^*\}$} &\text{all relevant choice nodes are indistinguishable for Player 2}\\
&Z=\{1^{\#},2^{\#},...,(|A_1| \times |A_2|)^\# \}\\
&\underline{i}= \begin{cases}
\{1^*\} \rightarrow 1 \\
H-\{1\} \rightarrow 2 \end{cases} & \text{at root Player 1, at all other choice nodes Player 2}\\
&\underline{A}= \begin{cases}
\{1^*\}\rightarrow A_1  \\
H-\{1\} \rightarrow A_2 \end{cases} & \text{at root the set of Player 1's actions, at all other choice nodes Player 2's}
\end{align*}
The successor function and the utility function are a little trickier. To avoid excessive formalism, I will use mostly prose.\\
First, $\sigma$ maps from the root to a different element of $H$ for each action available to Player 1 at the root. As there is exactly one more element in $H$ than there are actions available to Player 1, every element except the root in $H$ will be mapped to exactly once.\\
Second, $\sigma$ maps from each element in $H$ except for the root to as many elements in $Z$ as Player 2 has actions available. Each element in $Z$ will thus be mapped to exactly by one combination of element in $H$ and action chosen by Player 2.\\
Third, the "action path" thus specified - from root to element in $H$ by Player 1's action, and from element in $H$ to unique element in $Z$ - corresponds to an action profile in the original normal-form game. There it was associated with a payoff for each player. Since the elements in $Z$ are uniquely determined by the the "action paths" we can simply use the original utility function $\boldsymbol{u}':\boldsymbol{A}\rightarrow \mathbb{R}$ to specify the extensive-form utility function $\boldsymbol{u}':Z\rightarrow \mathbb{R}$.\\

\noindent \textbf{Different, yet equivalent, extensive-forms}\\
Consider the following games $\boldsymbol{G},\boldsymbol{G'},\boldsymbol{G''}$ to see transforming to and from extensive-form can yield different extensive-forms. The two extensive-form games are equivalent in the sense that the players can choose the same strategies and all strategy profiles yield the same payoffs.

 \begin{figure}[H]
 	\begin{center}
    \small
    \begin{tikzpicture}[thin,
      level 1/.style={sibling distance=40mm},
      level 2/.style={sibling distance=25mm},
      level 3/.style={sibling distance=15mm},
      every circle node/.style={minimum size=1.5mm,inner sep=0mm}]
      
      \node[circle,draw,label=above:$1$] (root) {}
        child { node {$1,1$}
          edge from parent
            node[left] {$L$}}
        child { node [circle,fill,label=above:$2$] {}
          child { 
            node[circle,fill] (node-A) {}
              child {
                node {$1,1$}
                edge from parent
                  node[left] {$X$}}
              child {
                 node {$8,5$}
                 edge from parent
                   node[right] {$Y$}}
              edge from parent
                node[left] {$A$}}
          child { 
            node[circle,fill] (node-B) {}
              child {
                node {$4,6$}
                edge from parent
                  node[left] {$X$}}
              child {
                 node {$2,1$}
                 edge from parent
                   node[right] {$Y$}}
              edge from parent
                node[right] {$B$}}
           edge from parent
             node[right] {$R$}};
      \draw [dashed] (node-A) -- (node-B) 
         node[midway,above] {$1$};
    \end{tikzpicture}
    \end{center}
    \caption{Extensive-form game $\bm{G}$}
  \end{figure}
\begin{table}[H]
\centering
\caption{Normal-form game $\bm{G'}$}
\label{my-label}
\begin{tabular}{|l|l|l|}
\hline
      & $A$   & $B$ \\ \hline
$L,X$ & 1, 1 & 1, 1     \\ \hline
$L,Y$ & 1, 1     & 1, 1  \\ \hline
$R,X$ & 1, 1      & 4, 6    \\ \hline
$R,Y$ &  8, 5     & 2, 1    \\ \hline
\end{tabular}
\end{table}
 \begin{figure}[H]
 	\begin{center}
    \small
    \begin{tikzpicture}[thin,
      level 1/.style={sibling distance=40mm},
      level 2/.style={sibling distance=25mm},
      level 3/.style={sibling distance=15mm},
      every circle node/.style={minimum size=1.5mm,inner sep=0mm}]
      
      \node[circle,draw,label=above:$1$] (root) {}
        child { node [circle,fill,label=above:$2$] {}
          child { 
            node [circle,fill] (node-C) {}
            	child {
            		node {$1,1$}
            		edge from parent
            			node [left] {$X$}}
            	child {
            		node {$1,1$}
            		edge from parent
            			node [right] {$Y$}}
				edge from parent              	
              	node[left] {$A$}}
          child { 
            node [circle,fill] (node-D) {}
            	child {
            		node {$1,1$}
            		edge from parent
            			node [left] {$X$}}
            	child {
            		node {$1,1$}
            		edge from parent
            			node [right] {$Y$}}
            	edge from parent
              	node[right] {$B$}}
          edge from parent
            node[left] {$L$}}
        child { node [circle,fill,label=above:$2$] {}
          child { 
            node[circle,fill] (node-A) {}
              child {
                node {$1,1$}
                edge from parent
                  node[left] {$X$}}
              child {
                 node {$8,5$}
                 edge from parent
                   node[right] {$Y$}}
              edge from parent
                node[left] {$A$}}
          child { 
            node[circle,fill] (node-B) {}
              child {
                node {$4,6$}
                edge from parent
                  node[left] {$X$}}
              child {
                 node {$2,1$}
                 edge from parent
                   node[right] {$Y$}}
              edge from parent
                node[right] {$B$}}
           edge from parent
             node[right] {$W$}};
      \draw [dashed] (node-A) -- (node-B) 
         node[midway,above] {$1$};
      \draw [dashed] (node-C) -- (node-D) 
         node[midway,above] {$1$};
    \end{tikzpicture}
    \end{center}
    \caption{Extensive-form game $\bm{G''}$}
  \end{figure}
\section*{Question 3}
Take any partial profile $\bm{\alpha_{-i}}$ of pure strategies for the other players. Given any behavioral strategy $s_i^*$ for player $i$ we want to find an outcome equivalent mixed strategy $s_i$. \\
Given the partial profile $\bm{\alpha_{-i}}$ and some behavioral strategy $s_i^*$ any leaf of the game-tree has a known probability of being reached. We now need to find the element $s_i$ of the set of all possible mixed strategies $\Pi$ which assigns the exact same probability to arriving at the specific leaf of our game-tree as the behavioral strategy. If $t$ is any leaf of the game tree, our mixed strategy needs to satisfy that $p(t|s_1^*,\bm{\alpha_{-1}}) = p(t|s_1,\bm{\alpha_{-1}})$.

\noindent First, observe that any leaf is is reachable by a unique path from the root (property of trees, $\sigma$ is injective etc.).\\
Given any leaf $t$, there is a unique path $K_t$ from the root to $t$. We can compute the probability of $K_t$ being followed under the full profile $\bm{\alpha}=(\bm{\alpha_{-i}},s_i^*)$. We do so by multiplying $s_i^*(h)(a)$ for all nodes where $i$ gets to play and the respective action $a$ that corresponds to $K_t$, then we multiply the probabilities of player $i$ playing the actions on $K_t$ under $s_i^*$ with the probabilities  of the other players playing the actions on $K_t$ where they get to choose- either $1$ or $0$. Thus we arrive at $p(t|s_1^*,\bm{\alpha_{-1}})$. We can do this for every leaf $z\in Z$ and its corresponding path $K_z$. \\
Given some $\bm{\alpha_{-1}}$, we can then define a mixed strategy for player $i$ that is outcome-equivalent to the behavioral strategy, by specifiying with which probability she will choose exactly that pure strategy $\alpha_i$ that leads to $t$. Concretely, the actions taken by $i$ on $K_t$ constitute the pure strategy $\alpha_i$ and the probability of playing it in $s_i$ is computed by multiplying the probabilities of playing the actions in $\alpha_i$ where $i$ gets to decide in $s_i^*$.\\
We can thus find an outcome-equivalent mixed strategy for any given behavioral strategy.

$A_i$ is the set of agent $i$'s pure strategies.\\

\end{document}